### 2024-04-14 nondirectional_ms_2024.Rmd
Update the manuscript and add references

On the face of it, pronounced individual differences in unconscious processing effects on cognition and perception seem possible, even likely. Indeed, previous investigations revealed heterogeneity in susceptibility to the attentional blink [@martens2006a], in the effects of stimulus onset asynchrony (SOA) on metacontrast masking [@albrecht2010a], the speed of breaking perceptual suppression [@sklar2021a], both in the breaking continuous flash suppression paradigm (b-CFS; [@jiang2007a] and the breaking repeated mask suppression one (b-RMS; [@abir2020a], and in the effects of visual imagery on conscious perception in a binocular rivalry setting [@dijkstra2019a]. Some qualitative differences have been linked to variability in processing speed [@martens2006a], genetics [@maksimov2013a], and brain anatomy and physiology [@gaal2011a; @boy2010a]. Critically, in other behavioural paradigms, unconscious stimuli had opposite effects on different participants. Bolger and colleagues [-@bolger2019a] showed that while most participants responded faster to upright faces in a b-CFS task, some responded faster to upside-down faces. Other findings from several different study groups have repeatedly revealed that masked priming effects changed in magnitude and even flipped in sign as a function of the interval between prime and target [@boy2014a; @boy2010b; @parkinson2014a; @schlaghecken2004a]. Moreover, different hypotheses were laid out over the years regarding the driving mechanisms of the counter-intuitive 'negative' priming effects. Among others, response inhibition of initial prime activations [@eimer2003a; @boy2010c], or neural habituation [@jacob2021a] were suggested. Taken together, it is not clear if, and to what extent, unconscious effects are subject to meaningful individual variability. Crucially, if they are, then some previously reported null results might actually be true effects, masked by such variability.

@@

We had three inclusion criteria: first, since all probed tests require trial-level data, only open-access datasets providing such data were included. Second, the independent variable of all studies had to be manipulated within single participants. And third, at least one non-significant effect was reported in the original study. Overall, this search strategy yielded data associated with `r n_empiric_ns` null effects (see Appendix B for details about all effects), 21 focusing on differences in RT and 5 on differences in signal detection sensitivity, d’ [@green1966a]. We used the criteria set by the original authors for demonstrating unawareness (e.g., using objective and/or subjective measures of awareness), and a two-sided non-parametric sign-flipping test on the population mean for filtering out significant priming effects^[Across all RT effects, our analysis used raw RT scores, and thus our results diverged from the original results when log transformations were used (see the notes column in Appendix B for details)]. Finally, we excluded participants with fewer than five trials per experimental condition and/or zero variance in the dependent variable (e.g., when accuracy was measured). Together, these data allowed us to reexamine null unconscious processing effects using a non-directional approach that takes into account the potential for differences in effect signs when testing for group-level effects. We accordingly asked whether true effects of unconscious processing were masked by population heterogeneity in effect signs.

@@

## Acknowledgements
  We thank all researchers who shared their data with us: Doby Rahnev, Lucas Battich, Kirsten C. S. Adam, Natalie Biderman, Nathan Faivre, Sung-En Chien, Lina Skora, Fenja Mareike Benthien, Iris Zerweck, Mikko Hurme, Timo Stein, Liana Machado, and the Open Science Collaboration. Furthermore, we thank David Shanks for his feedback on an early version of this work. MM was funded by a post-doctoral research fellowships from All Souls College at the University of Oxford.

>>>>

On the face of it, pronounced individual differences in unconscious processing effects on cognition and perception seem possible, even likely. Indeed, previous investigations revealed heterogeneity in susceptibility to the attentional blink [@martens2006a], in the effects of stimulus onset asynchrony (SOA) on metacontrast masking [@albrecht2010a], the speed of breaking perceptual suppression [@sklar2021a], both in the breaking continuous flash suppression paradigm (b-CFS; [@jiang2007a] and the breaking repeated mask suppression one (b-RMS; [@abir2020a], and in the effects of visual imagery on conscious perception in a binocular rivalry setting [@dijkstra2019a]. Some qualitative differences have been linked to variability in processing speed [@martens2006a], genetics [@maksimov2013a], and brain anatomy and physiology [@gaal2011a; @boy2010a]. Critically, in other behavioural paradigms, unconscious stimuli had opposite effects on different participants. Bolger and colleagues [-@bolger2019a] showed that while most participants responded faster to upright faces in a b-CFS task, some responded faster to upside-down faces. Other findings from several different study groups have repeatedly revealed that masked priming effects changed in magnitude and even flipped in sign as a function of the interval between prime and target [@boy2014a; @boy2010b; @parkinson2014a; @schlaghecken2004a], or the presentation duration of stimuli rendered unconscious using either crowding [@faivre2011a] or CFS [@faivre2012a; @barbot2012a]. Moreover, different hypotheses were laid out over the years regarding the driving mechanisms of the counter-intuitive 'negative' priming effects. Among others, response inhibition of initial prime activations [@eimer2003a; @boy2010c], or neural habituation [@faivre2011a; @faivre2012a; @barbot2012a; @jacob2021a] were suggested. Taken together, it is not clear if, and to what extent, unconscious effects are subject to meaningful individual variability. Crucially, if they are, then some previously reported null results might actually be true effects, masked by such variability.

@@

We had three inclusion criteria: first, since all probed tests require trial-level data, only open-access datasets providing such data were included. Second, the independent variable of all studies had to be manipulated within single participants. And third, at least one non-significant effect was reported in the original study. Overall, this search strategy yielded data associated with `r n_empiric_ns` null effects (see Appendix B for details about all effects), 21 focusing on differences in RT and five on differences in signal detection sensitivity, d’ [@green1966a]. We used the criteria set by the original authors for demonstrating unawareness (e.g., using objective and/or subjective measures of awareness), and a two-sided non-parametric sign-flipping test on the population mean for filtering out significant priming effects^[Across all RT effects, our analysis used raw RT scores, and thus our results diverged from the original results when log transformations were used (see the notes column in Appendix B for details)]. Finally, we excluded participants with fewer than five trials per experimental condition and/or zero variance in the dependent variable (e.g., when accuracy was measured). Together, these data allowed us to reexamine null unconscious processing effects using a non-directional approach that takes into account the potential for differences in effect signs when testing for group-level effects. We accordingly asked whether true effects of unconscious processing were masked by population heterogeneity in effect signs. Importantly, while we aimed for collecting as many datasets as possible, this is not a systematic review or meta-analysis. Accordingly, we conducted searches using Google Scholar, targeting any study investigating unconscious processing, while reporting at least one null result. Accordingly, it should be noted that our sample might miss relevant datasets due to the lack of systematic approach.

@@

## Acknowledgements
  We thank all researchers who shared their data with us: Doby Rahnev, Lucas Battich, Kirsten C. S. Adam, Natalie Biderman, Nathan Faivre, Sung-En Chien, Lina Skora, Fenja Mareike Benthien, Iris Zerweck, Mikko Hurme, Timo Stein, Liana Machado, and the Open Science Collaboration. Furthermore, we thank David Shanks and Miguel A. Vadillo for their feedback on an early version of this work. MM was funded by a post-doctoral research fellowships from All Souls College at the University of Oxford.
